---
title: "PMLfinalproject"
author: "mt"
date: "Monday, May 25, 2015"
output: html_document
---

This is final project of practical machine learning course first of all data doenloaded from here:

The training data for this project are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv


```{r, comment=FALSE, results='hide',echo=TRUE}
library(ISLR); library(ggplot2); 
library(caret);library(ElemStatLearn)
training<-read.csv("pml-training.csv")
testing<-read.csv("pml-testing.csv")
```

trainning and validation data extracted as below in this project trainning data separated with 70% of data for training and 30% for validation of dataset. 
```{r, echo=TRUE}
set.seed(33833)
training$classe<-as.factor(training$classe)
inBuild <- createDataPartition(y=training$classe,
                               p=0.7, list=FALSE)
validation <- training[-inBuild,]; traindata <- training[inBuild,]
```

in the case of higher speed of training with parallel processing here package doParallel have been used as shown below

```{r}
library(doParallel)
registerDoParallel()
```

training data have been evaluated by random forest algorithm

```{r}
modfit <- train(classe ~.,method="rf", data=traindata)
pred <- predict(modfit,validation);
```

the conclusion have been illustrated with evaluation of confusionMatrix in validation data
```{r}
confusionMatrix(validation$classe,pred)$overall
```

