---
title: "Tufte Handout"
author: "John Smith"
date: "August 13th, 2014"
output: rmarkdown::tufte_handout
---

# Introduction

\newthought{It is a particular case of gamma distribution} [^Exponential_distribution].

The Tufte-\LaTeX\ [^tufte_latex] document classes define a style similar to the style Edward Tufte uses in his books and handouts. Tufte’s style is known for its extensive use of sidenotes, tight integration of graphics with text, and well-set typography. 

# Headings

This style provides a- and b-heads (that is, `#` and `##`), demonstrated above.
An error is emitted if you try to use `###` and smaller headings.

\newthought{In his later books}[^books_be], Tufte starts each section with a bit of vertical space, a non-indented paragraph, and sets the first few words of the sentence in small caps. To accomplish this using this style, use the `\newthought` command as demonstrated at the beginning of this paragraph.

# Figures

## Margin Figures

Images and graphics play an integral role in Tufte's work. To place figures or tables in the margin you can use the `fig.margin` knitr chunk option. For example:

```{r, fig.margin = TRUE, fig.cap = "Sepal length vs. petal length, colored by species"}
library(ggplot2)
qplot(Sepal.Length, Petal.Length, data = iris, color = Species)
```

Note the use of the `fig.cap` chunk option to provide a figure caption. You can adjust the proportions of figures using the `fig.width` and `fig.height` chunk options. These are specified in inches, and will be automatically scaled down to fit within the handout margin.

## Equations

You can also include \LaTeX\ equations in the margin by explicitly invoking the `marginfigure` environment.---
title: "statistical inference final project"
author: "Mohammad Pivezhandi"
date: "Friday, May 22, 2015"
output: rmarkdown::tufte_handout
---

# Introduction

The basic concept behind Central Limit Theorem(CLT) is that as increase occurs in number of  iid samples mean values of samples converges to standard normal state so the mean and standard deviation characteristic converges to population mean and standard deviation. in this report theoretical concept of Exponenntial distribution compared with results of Central Limit Theorem.


\newthought{In probability theory and statistics}[^Exponential_distribution], the exponential distribution (a.k.a. negative exponential distribution) is the probability distribution that describes the time between events in a Poisson process, i.e. a process in which events occur continuously and independently at a constant average rate. It is a particular case of gamma distribution. based on theory the expected value is $E[x]=1/\lambda$ and standard deviation of exponentioal distribution is $\sigma[x]=1/\lambda$.

```{r ,fig.height=4,fig.width=8, fig.fullwidth = TRUE, fig.align='center', echo = FALSE,fig.cap = "Comparison between Simulation and theoretical of Exponential distribution" }
set.seed(3)
lambda<-.2
sample<-40
for (n in c(sample)){
        temp <- matrix(rexp(n * 1000, rate=lambda), ncol = n)
        temp <- apply(temp, 1, mean)
        hist(temp, breaks=50, prob=TRUE,
        main="sample average with lambda=0.2",xlab="",col="coral3")
        dty <- density(temp)
        lines(dty,col="red",lty=1)
        xfit <- seq(range(temp)[1], range(temp)[2], length=length(dty$x))
        yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(sample)))
        lines(xfit, yfit, pch=22, col="blue", lty=2)
        abline(v=mean(temp), col="green",lwd=3, lty=3)
        abline(v=mean(temp), col="brown",lwd=3, lty=4)
        legend('topright', c("simulation", "theoretical","simulation average line", "theoretical average line"), lty=c(1,2,3,4), col=c("red", "blue", "green","brown"),
        title.adj = 10)
        }
```



In 1000 times of simulation the constructed sample average curve is with mean of about $5.011$
that in theory should be $5$ and standard deviation of about $0.780$ that in theory should be about $0.790$.

for evaluating the variation of sample normal distribution with the theoretical normal values Mean squered error in curve structure have been used as:
```{r, fig.margin = TRUE, fig.cap = "MSE Error Rate"}
sum(((dty$y-yfit)^2)/length(yfit))
```
\begin{marginfigure}
$$\displaystyle \ MSE =\frac{\displaystyle\sum_{n=0}^\infty (output-target)^2}{N}$$
\caption{MSE equation}
\end{marginfigure}

[^Exponential_distribution]: http://en.wikipedia.org/wiki/Exponential_distribution


\begin{marginfigure}
$$\frac{d}{dx}\left( \int_{0}^{x} f(u)\,du\right)=f(x).$$
\caption{An equation}
\end{marginfigure}

Note the use of the `\caption` command to add additional text below the equation.

## Full Width Figures

You can arrange for figures to span across the entire page by using the `fig.fullwidth` chunk option. 

```{r, fig.width = 10, fig.height = 2, fig.fullwidth = TRUE, fig.cap = "Full width figure"}
qplot(wt, mpg, data=mtcars, colour=factor(cyl))
```

Note the use of the `fig.width` and `fig.height` chunk options to establish the proportions of the figure. Full width figures look much better if their height is minimized.

## Main Column Figures

Besides margin and full width figures, you can of course also include figures constrained to the main column.

```{r, fig.cap = "Another figure"}
qplot(factor(cyl), mpg, data = mtcars, geom = "boxplot")
```

# Sidenotes

One of the most prominent and distinctive features of this style is the extensive use of sidenotes. There is a wide margin to provide ample room for sidenotes and small figures. Any use of a footnote will automatically be converted to a sidenote. ^[This is a sidenote that was entered using a footnote.] 

If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `\marginnote` command. \marginnote{This is a margin note.  Notice that there isn't a number preceding the note.}

Note also that the two footnote references (`tufte_latex` and `books_be`, both defined below) were also included in the margin on the first page of this document.

# Tables

You can use the **xtable** package to format \LaTeX\ tables that integrate well with the rest of the Tufte handout style. Note that it's important to set the `xtable.comment` and `xtable.booktabs` options as shown below to ensure the table is formatted correctly for inclusion in the document.

```{r, results='asis'}
library(xtable)
options(xtable.comment = FALSE)
options(xtable.booktabs = TRUE)
xtable(head(mtcars[,1:6]), caption = "First rows of mtcars")
```

[^Exponential_distribution]: http://en.wikipedia.org/wiki/Exponential_distribution
[^tufte_latex]: https://code.google.com/p/tufte-latex/
[^books_be]: http://www.edwardtufte.com/tufte/books_be









