---
title: "Regression Models Final Project"
author: "MP"
date: "September 27th, 2015"
output: rmarkdown::tufte_handout
---

# Executive Summary

This study is about the automobile industry. Looking at a data set of a collection of cars, exploring the relationship between a set of variables and miles per gallon (MPG) (outcome) implemented by some exploratory analysis. Finally a comparison between automatic and manual fuel consumption in automobiles illustrated. The result shows higher fuel consumption of automatic automobiles in comparison to manual automobiles.

# Headings

the basic goal of this study is to answering folowing questions:

1- Is an automatic or manual transmission better for MPG?

2- Quantify the MPG difference between automatic and manual transmissions?

Table 1 shows top 6 values of 2 mtcars features. 
```{r,echo=FALSE, results='asis'}
library(xtable)
options(xtable.comment = FALSE)
options(xtable.booktabs = TRUE)
xtable(head(mtcars[,c("mpg","am")]), caption = "First rows of mtcars")
```

The name of all predictors that simplified are as shown below:

1-    mpg         Miles/(US) gallon

2-	 cyl	 Number of cylinders

3-	 disp	 Displacement (cu.in.)

4-	 hp	 Gross horsepower

5-	 drat	 Rear axle ratio

6-	 wt	 Weight (lb/1000)

7-	 qsec	 1/4 mile time

8-	 vs	 V/S

9-	 am	 Transmission (0 = automatic, 1 = manual)

10-	 gear	 Number of forward gears

11-	 carb	 Number of carburetors

# Data Analysis
In Motor Trend Car Road Tests there are 10 aspects of automobile design and as shown in table below the significance of features in prediction of miles per galon consumption could be directly taken by the P-value rate.

The predictors that have lower than 0.05 P-values shows uncorrelation and independent features. Table 2 that shows the model of glm just The value of weight shows little significant feature and other variables are less important in comparison to other ones.

The basic strategy in model selection is using significant features in prediction procedure.
```{r,echo=TRUE, results='asis'}
library(xtable)
options(xtable.comment = FALSE)
options(xtable.booktabs = TRUE)
library(datasets)
data(mtcars)
fit <- glm(mpg~., data=mtcars)
```

```{r,echo=FALSE, results='asis'}
xtable(summary(fit)$coefficients,digits=4, caption = "significant features evaluation base on miles per galon prediction in generalized linear model ")
```
```{r, fig.margin = TRUE,fig.width = 5,fig.height = 4, fig.fullwidth = TRUE, fig.cap = "Miles Per Gallon versus Transmission Type"}
plot(mtcars$mpg, mtcars$am,
     xlab="Miles/(US) gallon",
     ylab="Transmission",
     bg="lightblue",
     col="black", cex=1.1, pch=21, frame=F)
abline(lm(am~mpg, data=mtcars), lwd=2)
```

The `am` predictor is about automatic or manual features and The P-value about `0.2340` shows high correlation with other featues in prediction of  mpg and low significancy.

The Miles Per Gallon residual plot versus Transmission is as Figure 1 and This figure shows high Fuel consumption in Automatic versus Manual Transmission.

The mean and standard mpg difference of both automatic and manual Transmission analysed as shown in Table 3 and shows that the mean of miles per gallon in manual automobile is about twice of its automatic counterpart. 
```{r,echo=F, results='asis'}
library(xtable)
options(xtable.comment = FALSE)
options(xtable.booktabs = TRUE)
amean<-mean(mtcars$disp[mtcars$am==1])
mmean<-mean(mtcars$disp[mtcars$am==0])
asd<-sd(mtcars$disp[mtcars$am==0])
msd<-sd(mtcars$disp[mtcars$am==1])
diff<-rbind(c(amean,asd),c(mmean,msd))
diff<-data.frame(diff)
colnames(diff)<-c("Mean Value","Standard Deviation")
rownames(diff)<-c("Automatic Transmission","Manual Transmission")
xtable(diff, caption = "The difference of two Transmission")

```
# Conclusion
In Illustrated figures proved that miles per gallon in automatic Transmisson is lower than manual Transmission so manual cars have lower fuel consumption in comparison to Automatic automobile. Mean value of miles per galon in both Transmission shows that mpg in Manual Transmission is two times larger than automatic counterpart.

#Appendix
For beter sense of the fuel consumption of two transmission the Boxplot illustrated in Figure 2 where clearly shows higher Miles Per Gallon in Manual transmission.
```{r,fig.width = 5,fig.height = 4, fig.fullwidth = TRUE, fig.cap = "Boxplot of Miles Per Gallon versus Transmission Type"}
plot(factor(mtcars$am),mtcars$mpg,pch=20,col="green",xlab="Automatic=0,Manual=1",ylab="Miles Per Gallon")
```




