---
title       : Miles Per Gallon (MPG) in Different Transmissions
subtitle    : 
author      : mt
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Miles Per Gallon (MPG) in different Transmissions

This study is about the automobile industry. Looking at a data set of a collection of cars, exploring the relationship between a set of variables and miles per gallon (MPG) (outcome) implemented by some exploratory analysis.

--- 
## Automatic and Manual Transmission comparison
The result shows higher fuel consumption of automatic automobiles in comparison to manual automobiles.
```{r, echo=TRUE}
mean(mtcars$disp[mtcars$am==1]) #Mean MPG in Automatic automobiles 
mean(mtcars$disp[mtcars$am==0]) #Mean MPG in Manual automobiles
```

---
## Automatic and Manual Transmission Base Plot
The result shows higher fuel consumption of automatic automobiles in comparison to manual automobiles.
```{r, echo=F}
plot(mtcars$mpg, mtcars$am,
     xlab="Miles/(US) gallon",
     ylab="Transmission",
     bg="lightblue",
     col="black", cex=1.1, pch=21, frame=F)
abline(lm(am~mpg, data=mtcars), lwd=2)
```


---
## Conclusion
- The Figure shows high Fuel consumption in Automatic versus Manual Transmission.
- Mean value of miles per galon in both Transmission shows that mpg in Manual Transmission is two times larger than automatic counterpart.






